\section{External Aspect}

The client for this project is Matthew Pike, and his start up company, based in China. He was looking for a developer to meet the requirements for building the first version of the main software for this new company, that software being Niceway.to. Last year, Matthew reached out to a pair of developers with this same purpose, but he was disappointed with the quality of the project, and its lack of completion. For this reason, he decided that he would scrap the original work, and begin from scratch, with a new developer.\ \\
\ \\
Communication with the client was initially facilitated through the supervisor for this project, Max L Wilson, who has a personal relationship with Matthew. After this point, a semi-frequent level of email communication was maintained by the client and I, at key points in the project. This was due to the client being based in China, and thus conflicting locality and time zones making face to face meetings, or even video calls, impossible to schedule. The table below summarises the main communication that took place throughout the course of the project, at the different stages, between the client and I.

\begin{center}
\begin{tabular}{p{2cm}|p{12cm}}
	\hline
	\textbf{Date} & \textbf{Items Discussed}\\
	\hline	
	\multicolumn{2}{l}{\textbf{Initial stages}}\\
	\hline
	1st Oct 15 & Initial specification received from client\\
	8th Oct 15 & Design specification with functional and non-functional requirements, initial designs, and market research provided to client\\	
	13th Oct 15 & Setting up of web host for server for Niceway.to \\
	15th Oct 15 & Project proposal shared with client \\
	\hline
	\multicolumn{2}{l}{\textbf{Development stage}}\\
	\hline
	9th Nov 15 & Report of progress: ability for users to create accounts and log into the system, as well as near completion of the route creation page \\
	29th Jan 16 & Report of progress: completion of the route search page, route detail page and the user profile page.\\
	\hline
	\multicolumn{2}{l}{\textbf{Project Completion}}\\	
	\hline		
	23rd Feb 16 & Report of progress: Completion of coding\\
	\hline	
	\end{tabular}	
\end{center}
\noindent 
As far as fulfilling the original intentions of the client, I feel like the project did this well. Almost all of the communication between my client and I was positive, and he was pleased with the speed and quality of the progress being made. As can be seen in section \ref{sec:testing} all functional and non-functional requirements of the system were adhered to, and there were even extra features included, that made the application easier to use for both the users, and the administrators. The usability tests also concurred that the system was easy to use, and users of all skills levels were able to understand and access the key areas and functionality of the site. From these tests it is clear to see that the website is ready for adoption by real users, which was an important aspect of the project for my client.\ \\
\ \\
The ``customers'' of the project were defined by my client as belonging in one of two main categories, both of which are catered to differently. The first group is the ``traveller'', who has minimal interaction with the site, and benefits mostly from the content provided by other users, therefore their journey through the search process should be as simple as possible. The second group is the ``experts'' group, who are active contributors to the website, are actively engaged with the site, and their passion is travelling. For these users, the content creation and sharing systems are most important. As a final note, there is no general demographic for the application, and instead it is developed to be accessible by all users, regardless of any identifiable characteristic.